\newpage

% mostly from reassessment-15

\section{Question}
\standards{
  \standard{pointers and references}
}

\begin{itemize}

  \item Write statements to do the following:
    \begin{itemize}
      \item Declare an \mintinline{cpp}{int} named \mintinline{cpp}{i} and set
        it equal to \mintinline{cpp}{3}.
      \item Declare a pointer named \mintinline{cpp}{p} and use it to set
        \mintinline{cpp}{i} equal to \mintinline{cpp}{4}.
      \item Declare a reference named \mintinline{cpp}{r} and use it to set
        \mintinline{cpp}{i} equal to \mintinline{cpp}{5}.
      \item Output the value of \mintinline{cpp}{i}, the value pointed to by
        \mintinline{cpp}{p}, and the value referenced by \mintinline{cpp}{r},
        separated by whitespace, and \textbf{indicate the results of this
        statement}.
    \end{itemize}
    \textAnswer{\showCodeLeft{pointers-1-1}{all}}
    \vfill

  \item Show the output of the following program:
    \evaluateCodeLeft{pointers-1-2}{all}

    \filbreak

  \item Show the output of the following program.  Recall that
    \mintinline{cpp}{uintptr_t} is an unsigned integer type capable of
    storing any valid pointer value without loss of precision, and that
    \mintinline{cpp}{(uintptr_t)a} is a C style cast of \mintinline{cpp}{a} to
    type \mintinline{cpp}{uintptr_t}.
    \evaluateCodeTop{pointers-1-3}{all}
    \vspace{3ex}

  \item List one similarity between an array and a pointer to the array's first
    element.
    \textAnswer{\par
      \begin{itemize}
        \item Either may be used to access any element of the array, with the
          same syntax.
        \item They both convert to the same integral value.
        \item $\cdots$
      \end{itemize}
    }
    \vfill

  \item List one difference between an array and a pointer to the array's first
    element.
    \textAnswer{\par
      \begin{itemize}
        \item They have different type.
        \item The pointer may be assigned to, whereas the array may not.
        \item Taking \mintinline{cpp}{sizeof(p)} and
          \mintinline{cpp}{sizeof(a)} (assuming the array is called
          \mintinline{cpp}{a} and the pointer is called \mintinline{cpp}{p})
          will give different results.
        \item $\cdots$
      \end{itemize}
    }
    \vfill

\end{itemize}

\newpage

