% -----------------------------------------------------------------------------
% Copyright &copy; 2015 Ben Blazak <bblazak@fullerton.edu>  
% This work is licensed under a [Creative Commons Attribution 4.0 International
% License] (http://creativecommons.org/licenses/by/4.0/)  
% -----------------------------------------------------------------------------

\input{document-setup.part.tex}

% -----------------------------------------------------------------------------

\begin{document}
\docCopyright

\section{Question}
\standards{
  \standard{history and culture :: general knowledge}
}

\subsection*{People}
In roughly 2 or 3 sentences, explain who each person is and what they did that
is relevant to our class.
\textQuestion{\makeDashedLine}
\begin{itemize}
  \item Ken Thompson
    \vfill\textQuestion{\makeDashedLine}
  \item Brian Kernighan
    \vfill\textQuestion{\makeDashedLine}
  \item Dennis Ritchie
    \vfill\textQuestion{\makeDashedLine}
  \item Bjarne Stroustrup
    \vfill\textQuestion{\makeDashedLine}
  \item Alan Kay
    \vfill
\end{itemize}

\newpage

\subsection*{Places}
In roughly 2 or 3 sentences, explain what happened at each of these places that is relevant to our class.
\textQuestion{\makeDashedLine}
\begin{itemize}
  \item MIT AI Lab (Hint: See the history section of the Wikipedia entry on
    object-oriented programming.)
    \vfill\textQuestion{\makeDashedLine}
  \item Xerox PARC
    \vfill\textQuestion{\makeDashedLine}
  \item AT\&T Bell Labs
    \vfill
\end{itemize}

\subsection*{Languages}
In roughly 2 or 3 sentences, explain why each of these programming languages is
relevant to our class.
\textQuestion{\makeDashedLine}
\begin{itemize}
  \item Simula
    \vfill\textQuestion{\makeDashedLine}
  \item Smalltalk
    \vfill
\end{itemize}

\newpage

\subsection*{Languages (continued)}
\textQuestion{\makeDashedLine}
\begin{itemize}
  \item Name at least 3 other object oriented programming languages.
    \vfill\textQuestion{\makeDashedLine}
  \item List the 3 (or 4) major programming language paradigms.
    \vfill
\end{itemize}

\subsection*{C++}
\textQuestion{\makeDashedLine}
\begin{itemize}
  \item Why are there both pointers and references in C++? (Hint: See Bjarne
    Stroustrup's C++ FAQ.)
    \vfill
    \vfill\textQuestion{\makeDashedLine}
  \item Why is \mintinline{cpp}{this} a pointer instead of a reference? (Hint:
    See Bjarne Stroustrup's C++ FAQ.)
    \vfill
    \vfill
\end{itemize}

\subsection*{Safety}
\textQuestion{\makeDashedLine}
\begin{itemize}
  \item What is ergonomics?  Why do we care?
    \vfill
    \vfill\textQuestion{\makeDashedLine}
  \item What is RSI?  Why do we care?  What can be done to prevent it?
    \vfill
    \vfill
    \vfill
\end{itemize}

\end{document}

