% -----------------------------------------------------------------------------
% Copyright &copy; 2015 Ben Blazak <bblazak@fullerton.edu>  
% This work is licensed under a [Creative Commons Attribution 4.0 International
% License] (http://creativecommons.org/licenses/by/4.0/)  
% -----------------------------------------------------------------------------

\input{document-setup.part.tex}

% -----------------------------------------------------------------------------

\begin{document}
\docCopyright

\section{Question}
\standards{
  \standard{visual studio}
}

Demonstrate the following using Visual Studio 2013\footnote{Since this is the
version currently in use for the Programming Lab Practicum}:
\begin{itemize}
  \item project with multiple \mintinline{text}{.h} and \mintinline{text}{.cpp}
    files
    \begin{itemize}
      \item Begin with an empty project.
      \item Create a file named \mintinline{cpp}{function.h}, and place in it a
        prototype for a \mintinline{cpp}{void} function that takes one argument
        (of your favorite type) and prints it to \mintinline{cpp}{stdout}.
      \item Create a file named \mintinline{cpp}{function.cpp}, and place in it
        the definition of the function prototyped in
        \mintinline{cpp}{function.h}.
      \item Create a file named \mintinline{cpp}{main.cpp}, and place in it the
        definition of \mintinline{cpp}{main()}.  Your \mintinline{cpp}{main()}
        function should call the function prototyped in
        \mintinline{cpp}{function.h}.
    \end{itemize}
  \item file I/O
    \begin{itemize}
      \item Use Notepad to create a text file, containing a single integer,
        on the Desktop.
      \item Move the file wherever you like (or don't move it at all).
      \item In the \mintinline{cpp}{main()} function written above, open the
        file.
      \item Read the integer from the file.
      \item Print it to \mintinline{cpp}{stdout}.
      \item Close the file.
      \item Open a new file for writing.
      \item Print \mintinline{cpp}{"hello world\n"} to the file.
      \item Close the file.
      \item Move the file to the Desktop (if it is not already there).
    \end{itemize}
\end{itemize}

\end{document}

