% -----------------------------------------------------------------------------
% Copyright &copy; 2015 Ben Blazak <bblazak@fullerton.edu>  
% This work is licensed under a [Creative Commons Attribution 4.0 International
% License] (http://creativecommons.org/licenses/by/4.0/)  
% -----------------------------------------------------------------------------

\input{document-setup.part.tex}

% -----------------------------------------------------------------------------

\begin{document}
\docCopyright

\standardsSection{
  \standard{interfaces}
}

\newEvenPage

\section{Question}
\standards{
  \standard{interfaces}
}

Recall that an interface is an abstract class, and an abstract class is a class
with at least one pure \mintinline{cpp}{virtual} method.

Before you begin, please
\begin{itemize}
  \item Be sure to place at the top of your answer any necessary
    \mintinline{cpp}{#include} directives or \mintinline{cpp}{using}
    statements.
  \item Remember to preface your interface with a block comment containing a
    short description of what it is intended to represent or be used for, etc.
  \item Remember to include a \mintinline{cpp}{virtual} destructor with a
    default inline implementation.  \textbf{All interfaces classes should have
    a \mintinline{cpp}{virtual} destructor.}
  \item Be sure to write your answers neatly and in a good and consistent
    style.  This will be graded.  I recommend writing out your solution on
    scratch paper, and then copying it to the following page.  You might also
    consider using pencil, if pen is your usual choice.
  \item Try to comment with the level of detail you would find helpful (but not
    irritating) in code of similar complexity written by another student in
    this class.
\end{itemize}

Write an interface for an \mintinline{cpp}{Automobile} having the following
\mintinline{cpp}{private} data members (all of type \mintinline{cpp}{float}):

\begin{itemize}
  \item \mintinline{cpp}{fuel}
  \item \mintinline{cpp}{speed}
\end{itemize}

Write \mintinline{cpp}{virtual} getters and setters, with inline
implementations, for each private data member.

Write declarations for at least two of the following pure
\mintinline{cpp}{virtual} methods (all of which take no arguments and return
\mintinline{cpp}{void}):
\begin{itemize}
  \item \mintinline{cpp}{turnLeft}
  \item \mintinline{cpp}{turnRight}
  \item \mintinline{cpp}{raiseHydraulics}
  \item \mintinline{cpp}{spinRims}
\end{itemize}

\newpage

\textQuestion{\makePageQuadrilleRuled}
\textAnswer{\inputminted{cpp}{\docCodeDir/.interfaces.cpp.gen.section.all}}

\end{document}

