% -----------------------------------------------------------------------------
% Copyright &copy; 2015 Ben Blazak <bblazak@fullerton.edu>  
% This work is licensed under a [Creative Commons Attribution 4.0 International
% License] (http://creativecommons.org/licenses/by/4.0/)  
% -----------------------------------------------------------------------------

\input{document-setup.part.tex}

% -----------------------------------------------------------------------------

\begin{document}
\docCopyright

\standardsSection{
  \standard{inheritance}
}

\newEvenPage

\section{Question}
\standards{
  \standard{inheritance}
}

Before you begin, please
\begin{itemize}
  \item Be sure to place at the top of your answer any necessary
    \mintinline{cpp}{#include} directives or \mintinline{cpp}{using}
    statements.
  \item Remember to preface your program with a block comment containing a
    short description of what it is intended to do.
  \item Be sure to write your answers neatly and in a good and consistent
    style.  This will be graded.  I recommend writing out your solution on
    scratch paper, and then copying it to the following page.  You might also
    consider using pencil, if pen is your usual choice.
  \item Try to comment with the level of detail you would find helpful (but not
    irritating) in code of similar complexity written by another student in
    this class.
\end{itemize}

Write a \mintinline{cpp}{Rectangle} class with the following
\mintinline{cpp}{private} data members (as \mintinline{cpp}{float}s):
\begin{itemize}
  \item \mintinline{cpp}{length}
  \item \mintinline{cpp}{width}
\end{itemize}
and the following \mintinline{cpp}{public} members (defined inside the class):
\begin{itemize}
  \item A constructor that takes two \mintinline{cpp}{float}s as arguments, and
    uses them to initialize the class's \mintinline{cpp}{private} data members
    (using the initialization list).
  \item A \mintinline{cpp}{const} method named \mintinline{cpp}{area} that
    takes no arguments, and returns the area of the rectangle as a
    \mintinline{cpp}{float}.
\end{itemize}

Next, write a \mintinline{cpp}{Square} class that inherits from
\mintinline{cpp}{Rectangle} and has the following \mintinline{cpp}{public}
members (defined inside the class):
\begin{itemize}
  \item A constructor that takes one \mintinline{cpp}{float} as an argument,
    and passes it to the parent constructor such that the inherited private
    data members are properly initialized.
\end{itemize}

Finally, write a \mintinline{cpp}{main} function that creates a
\mintinline{cpp}{Rectangle} and a \mintinline{cpp}{Square}, and uses them to
generate the following output:
\inputminted[label=Output]{text}{\docCodeDir/.inheritance.gen.output.gen.section.all}

\newpage

\textQuestion{\makePageQuadrilleRuled}
\textAnswer{\inputminted{cpp}{\docCodeDir/.inheritance.cpp.gen.section.all}}

\newOddPage

\textQuestion{\makePageQuadrilleRuled}
\textAnswer{~}

\end{document}

