% -----------------------------------------------------------------------------
% Copyright &copy; 2015 Ben Blazak <bblazak@fullerton.edu>  
% This work is licensed under a [Creative Commons Attribution 4.0 International
% License] (http://creativecommons.org/licenses/by/4.0/)  
% -----------------------------------------------------------------------------

\input{document-setup.part.tex}

% -----------------------------------------------------------------------------

\begin{document}
\docCopyright

\section{Question}
\standards{
  \standard{memory management and dynamic memory}
}

\begin{itemize}

  \item Given a \mintinline{cpp}{const int SIZE} set to some positive value,
    use either the C style functions or the C++ style operators to write
    statements to do the following:
    \begin{itemize}
      \item Dynamically allocate memory for an array of \mintinline{cpp}{SIZE}
        \mintinline{cpp}{double}s, and store the resulting pointer to the first
        element in a variable of the appropriate type.
      \item Deallocate the dynamically allocated memory.
    \end{itemize}
    \textAnswer{\inputminted{cpp}{\docCodeDir/.memory.cpp.gen.section.all}}
    \vfill

  \item In what section of memory are automatic variables placed?
    \textAnswer{\par
      the stack
    }
    \vfill

  \item In what section of memory are dynamically allocated variables placed?
    \textAnswer{\par
      the heap (when using C style functions) or the free store (when using C++
      style operators) (though the free store is often informally referred to
      as the heap)
    }
    \vfill

  \item What happens when you dynamically allocate memory, but fail to
    deallocate it?
    \textAnswer{\par
      The memory remains allocated to your program until the program is
      terminated (at which time \textit{all} memory in use by your program is
      reclaimed by the operating system).  This is known as a memory leak.
    }
    \vfill

  \item What happens when you deallocate a block of dynamically allocated
    memory, but keep a pointer to the beginning of the block?
    \textAnswer{\par
      The pointer may still be used in some ways, but dereferencing it leads to
      undefined behavior.  This is known as a dangling pointer.
    }
    \vfill

\end{itemize}

\end{document}

